R Notebook

### 2022-03-31 Code/Simulation.Rmd
Added temporary captions to figures for parameters

# Set variables
n <- 100
rho <- 0.7
counter <- 0
nrep <- 1000
B <- 100

@@

# Generate histograms plot
hist_copula_gamma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

@@

hist_copula_gamma
```

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 100

@@

# Generate histograms plot
hist_copula_gev <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")

>>>>

# Set variables
n <- 100
rho <- 0.7
counter <- 0
nrep <- 1000
B <- 100
shape <- 3
scale <- 1

@@

# Generate histograms plot
hist_copula_gamma <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("Rho = %s, Shape = %s, Scale = %s", rho, shape, scale))

@@

hist_copula_gamma

# Save the histogram figure
ggsave(filename = "hist_copula_gamma.pdf", plot = hist_copula_gamma, path = "../Manuscript", height = 2.1, width = 6)
```

@@

# Set variables
n <- 100
rho <- 0.5
counter <- 0
nrep <- 1000
B <- 100
loc <- 0
shape <- 1
scale <- 1

@@

# Generate histograms plot
hist_copula_gev <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y") +
                   labs(caption = sprintf("Rho = %s, Loc = %s, Shape = %s, Scale = %s", rho, loc, shape, scale))
